\newpage
\pagestyle{empty} % Remove page numberings while keeping hyperref happy
\begin{singlespace}
{\parindent0pt % disables indentation
{\large Douglas Wong}\hfill{douglas.kt.wong@gmail.com}\\ \null \hfill{github.com/dougUCN}

%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{\baselineskip}
{\large Education}\vspace{0.25\baselineskip}\hrule\vspace{0.75\baselineskip}

\textbf{Indiana University Bloomington}

\textit{PhD, Physics}\hfill\textit{2016 -- 2023}

\vspace{\baselineskip}

\textbf{Yale University}

\textit{BS, Physics}\hfill\textit{2012 -- 2016}

%%%%%%%%%%%%%%%%%%%%%%%%
%     Research
%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{\baselineskip}
{\large Research} \vspace{0.25\baselineskip}\hrule\vspace{0.75\baselineskip}

\textbf{Indiana University Bloomington}

\textit{Graduate student with Dr. Chen-Yu Liu}\hfill\textit{2016 -- 2023}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Performed instrumentation development and data analysis for the neutron electric dipole moment (nEDM) experiment at Los Alamos National Laboratory (LANL), which uses ultracold neutrons (UCN) to probe for new sources of time-reversal symmetry violation and gives clues to the puzzle of matter-antimatter asymmetry in the universe.
    \item Using Python, developed multiple libraries for the control of scientific devices in the LANL nEDM experiment. This includes a custom UDP protocol for a 250MHz analog-to-digital data collection system.
    \item Created a comprehensive Monte Carlo simulation in C++ of the entire LANL nEDM experiment. This simulation was run on the high-performance computing (HPC) cluster at Indiana University, and was capable of emulating millions of neutron trajectories and interactions.
\end{itemize}

\vspace{\baselineskip}
\textbf{Los Alamos National Laboratory}

\textit{DOE Office of Science Graduate Student Research Awardee with Dr. Takeyasu Ito}\hfill\textit{2020 -- 2021}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Assisted in the construction and development of the LANL nEDM experimental beamline
    \item Collected and analyzed data regarding UCN transport and UCN spin transport, including the development of an analytical model describing storage of UCN.
\end{itemize}

\vspace{0.5\baselineskip}

\textit{SULI undergraduate researcher with Dr. Andy Saunders}\hfill\textit{Summer 2015}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Using C++ and the CERN ROOT Data Analysis Framework, simulated neutron trajectories within the UCN$\tau$ neutron life-time experiment for analysis of chaotic particle orbits 
\end{itemize}

\vspace{\baselineskip}
\textbf{Yale University}

\textit{Undergraduate researcher with Dr. Steven Lamoreaux}\hfill\textit{2013 -- 2016}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed a distance measurement method for Casimir force experiments based on a capacitive bridge technique, which enabled high-speed, in-situ measurement of distances from 0.5--\qty{10}{\micro m} 
\end{itemize}

\vspace{0.5\baselineskip}

\textit{Undergraduate researcher with Dr. Jo Handelsman (Biology)}\hfill\textit{2012 -- 2013}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Using shotgun genetic sequencing, built metagenomic libraries and performed functional screens to detect the presence of aminoglycoside antibiotic resistance in Puerto Rican soil samples
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%
%     Volunteering
%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{\baselineskip}
{\large Volunteering}\vspace{0.25\baselineskip}\hrule\vspace{0.75\baselineskip}

\textbf{ArtRacks New Haven}\hfill\textit{2012 -- 2016}
\begin{itemize}[noitemsep,topsep=0pt]
    \item Cofounded an organization to construct and install custom, public bike racks at local libraries, schools, medical centers, and businesses free of cost. 
    \item Coordinated efforts with Yale students and community artists to design and build bike racks. Communicated with the New Haven Department of Transportation to gain approval and clear administrative requirements for bike rack installation
    \item Responsible for procuring multiple rounds of funding from Yale University, Design for America, and the city of New Haven
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%
%     Publications
%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{\baselineskip}
{\large Publications}\vspace{0.25\baselineskip}\hrule
\setlength{\biblabelsep}{-10pt}
\begin{refsection} 
    \nocite{wong_north_beamline_2023}
    \nocite{lamoreaux_wong_casimir_2015}
    \printbibliography[heading=none]
\end{refsection} 

%%%%%%%%%%%%%%%%%%%%%%%%
%     Presentations
%%%%%%%%%%%%%%%%%%%%%%%% 
{\large Presentations}\vspace{0.25\baselineskip}\hrule\vspace{0.75\baselineskip}

Physics of Fundamental Symmetries and Interactions Workshop. \textit{The neutron electric dipole moment experiment at Los Alamos National Laboratory}. (Paul Scherrer Institute, Switzerland. Nov 2022)

\vspace{0.25\baselineskip}

American Physical Society April Meeting 2022. \textit{Status of the development of the LANL nEDM Experiment}. (New York City, NY. and online April 2022)

\vspace{0.25\baselineskip}

International Workshop on Searches for the Electric Dipole Moment. \textit{Ultra cold neutron transport for the Neutron Electric Dipole Moment Search at Los Alamos National Laboratory}. (Les Houches School of Physics, Online. Feb 2021)

\vspace{0.25\baselineskip}

American Physical Society April Meeting 2020. \textit{Ultracold Neutron Density for the Neutron Electric Dipole Moment Search at Los Alamos National Laboratory}. (Online. April 2020)

\vspace{0.25\baselineskip}

FRIB TA Topical Program: Hadronic Electric Dipole Moments in the FRIB Era: From the Proton to Protactinium. \textit{Simulations of neutron spin manipulation and transport for the LANL neutron EDM experiment}. (East Lansing, MICH. Aug 2019) 

%%%%%%%%%%%%%%%%%%%%%%%%
%     Awards
%%%%%%%%%%%%%%%%%%%%%%%% 
\vspace{\baselineskip}
{\large Awards}\vspace{0.25\baselineskip}\hrule\vspace{0.75\baselineskip}

U.S. Department of Energy Office of Science Graduate Student Research Award\hfill\textit{2020}

\vspace{0.25\baselineskip}

Design for America Impact Grant (for ArtRacks New Haven)\hfill\textit{2015}

\vspace{0.25\baselineskip}

New Haven Mayor's Community Arts Grant (for ArtRacks New Haven)\hfill\textit{2014}

\vspace{0.25\baselineskip}

Yale College Dean's Research Fellowship\hfill\textit{2014}

\vspace{0.25\baselineskip}

Yale College Freshman Summer Research Fellowship in the Sciences \& Engineering\hfill\textit{2013}


} % resume normal indentation
\end{singlespace}
